\section{Publications}

\begin{supertabular}{p{1.8cm}|p{12cm}}
	\textsc{May 2020} & Neural machine translation for South Africa's official languages \\
	& \small{L Martinus, \textbf{J Webster}, J Moonsamy, M Shaba, R Moosa, R Fairon, \emph{Workshop paper at AfricaNLP, ICLR 2020}} \\
	& \footnotesize{Calculated a benchmark translation score for all of South Africa's official languages using state of the art neural machine translation techniques. These were the first such scores published at the time.} \\
	\multicolumn{2}{c}{} \\
	\textsc{Apr 2019} & Coiling free electron matter waves \\
	& \small{J Pierce, \textbf{J Webster}, H Larocque, E Karimi, B McMorran, A Forbes, \emph{New Journal of Physics 21 (4), 043018}} \\
	& \footnotesize{Demonstrated the construction of a novel class of angularly accelerating electron beams. Provided the means to construct the beam, while my collaborators performed the experiment. Contributed to the theoretical analysis of the electromagnetic field during the electron’s propagation. This paper was based on work from my Honours thesis.} \\
	\multicolumn{2}{c}{} \\
	\textsc{Jun 2018} & Subexponentially Growing Hilbert Spaces and Nonconcentrating Distributions in a Constrained Spin Model \\
	& \small{\textbf{J Webster}, M Kastner, \emph{Journal of Statistical Physics 171.3 (2018): 449-461}} \\
	& \footnotesize{Studied a highly constrained long-range spin model for use in a specially prepared Bose-Einstein condensate experiment. Resulted from the work done during my internship at NITheP.} \\
	\multicolumn{2}{c}{} \\
	\textsc{Jan 2017} & Radially dependant angular acceleration of twisted light \\
	& \small{\textbf{J Webster}, C Rosales-Guzm\'an, A Forbes, \emph{Optics letters 42.4 (2017): 675-678}} \\
	& \footnotesize{Developed a new technique of controlling the angular acceleration of laser light by using the Guoy phase in Laguerre-Gauss beams. This paper was featured as one of the top downloads on OSA’s website during February 2017.} \\
\end{supertabular}