\section{Work Experience}

\begin{supertabular}{p{1.8cm}|p{12cm}}
	\textsc{Mar 2020 -}  		& Data Scientist at \textsc{Percept Solve} \\
	\textsc{Present}			& \emph{Consulting} \\
								& \footnotesize{Provided mathematical analysis and machine learning solutions to a variety of business and government problems. Built and maintained full-stack web products for internal and client use. Worked in a diverse multi-disciplinary team of health economists, actuaries, and data scientists. Mathematically modelled and was the technical lead for the ASSA Covid 19 model (see Projects).} \\
	\multicolumn{2}{c}{} \\
	\textsc{Jan 2019 --}  		& Data Science Course Facilitator at \textsc{Explore-AI} \\
	\textsc{Mar 2020}			& \emph{Teaching and Consulting} \\
								& \footnotesize{Course facilitator for 100 data science students in Johannesburg. One of the AWS system administrators for the academy and facilitators. Designed and implemented curriculum for online courses. Supervised 4 teams of interns positioned at and consulting with a multitude of different companies. Organized a monthly meetup event (see Leadership).} \\
	\multicolumn{2}{c}{} \\
	\textsc{Jan 2017 -}  		& Lab Assistant at \textsc{Stellenbosch University} \\
	\textsc{Dec 2018}			& \emph{Ion trapping and spectrometry} \\
								& \footnotesize{Lab assistant in the ion trapping unit of Stellenbosch's Physics department. Work done as part of my Master's thesis. Mathematically modelled atomic quadrupole transitions via light possessing orbital angular momentum. received top honours and awarded the S2A3 medal for best Master's thesis in the faculty of science.} \\
	\multicolumn{2}{c}{} \\
	%\textsc{Jan - Dec 2016} 	& 2\textsuperscript{nd} year Tutor for the \textsc{University of the Witwatersrand} \\
	%							& \emph{Classical Mechanics and Electrodynamics} \\
	%							& \footnotesize{Was tasked with giving tutorial sessions and marking student scripts for the 2\textsuperscript{nd} year Physics Major students. Learned to teach in front of a large crowd.} \\
	\multicolumn{2}{c}{} \\
	\textsc{Jun 2016 --}    	& Research Collaborator at \textsc{University of Oregon} \\
	\textsc{Jul 2016}			& \emph{Reference:} Dr.\ Ben McMorran | \email{mcmorran@uoregon.edu}\\
	 							& \footnotesize{Developed new methods of generating electron vortex beams, and was trained to operate a transmission electron microscope. Helped form new collaborations between my research group and that of Ben McMorran’s.}\\
	\multicolumn{2}{c}{} \\
	% \multicolumn{2}{c}{} \\  % DUPLICATED FOR AESTHETIC REASON, REMOVE!!!!!!
	\textsc{Dec 2015 --} 		& Intern at the \textsc{National Institute for Theoretical Physics (NITheP)} \\
	\textsc{Jan 2016} 			& \emph{Reference:} Prof.\ Michael Kastner | \email{kastner@sun.ac.za}\\
	 							& \footnotesize{Studied a long-range highly constrained spin model that has shown equivalence to certain Bose-Einstein condensates. Learned to tackle extremely technical and challenging theoretical problems, and learned a great deal of quantum mechanics and statistical physics in the process.}\\
	\multicolumn{2}{c}{} \\
	\textsc{Jul 2012 --} 		& Intern at the \textsc{Council for Scientific and Industrial Research (CSIR)} \\
	\textsc{Dec 2014}			& \emph{Reference:} Dr.\ Hermann Uys | \email{hermann@sun.ac.za}\\
	 							& \footnotesize{Interned throughout various summer and winter vacations. Was tasked with a number of projects, including: building a large-scale ion trap for use in public demonstrations, simulating the motion of trapped ions, and investigating rotational broadening effects on molecular spectra.} \\
\end{supertabular}